Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance

### 2013-03-15 paper/ms.tex
updated to include and construct Fig2

\begin{figure}
\begin{center}
%\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
  $P>0.1$\label{figure:landscape}.} 
\end{figure}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P99.pdf}\\
\vspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_full_P5.pdf}
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
  $P>0.05$\label{figure:landscape}.} 
\end{figure*}
